\addskill%
{%
    \underline{Languages}:%
    \begin{multicols}{2}
        \begin{itemize}[nosep, rightmargin=0cm,after*={\vspace{-\baselineskip}}]%
            \item {\em My mothertonge}: mother tongue.
            \item {\em Some other language}: fluent (C2).
            \columnbreak
            \item {\em Some other language}: intermediate/good (B2).
            \item {\em Some other language}: basic knowledge (A1).%
        \end{itemize}%
    \end{multicols}
}%

\addskill%
{%
    \underline{Some knowledge field}:%
    \begin{itemize}[nosep, rightmargin=0cm]%
        \item Some topic.
        \item Another topic.
        \item Some other topic.
    \end{itemize}%
}%

\addskill%
{%
    \underline{Another knowledge field}:%
    \begin{itemize}[nosep, rightmargin=0cm]%
        \item Some topic.
        \item Another topic.
        \item Some other topic.
    \end{itemize}%
}%

\addskill%
{%
    \underline{Computer and programming}:%
    \begin{itemize}[nosep, rightmargin=0cm]%
        \item Languages: Assembly, C/C++, Python, Bash, Java, MySQL.%
        \item Libraries: Boost, Xlib, GTK+, QT, OpenGL, GLU, GLUT, POSIX Threads,\\Berkeley sockets, OpenSSL, Unix Signals.%
        \item Parallel/distributed: CUDA, OpenMP, OpenCL, OpenMPI.%
        \item Machine learning: Caffe, R, scikit-learn, TensorFlow, tSNE, WEKA.%
        \item Scientific: NI LabVIEW, MATLAB/Simulink, Octave, Scilab, Maxima,\\gnuplot, Eigen, GSL, ODE.
        \item Robotics: Gazebo, V-REP, ROS, KDL, VICON motion capture system,\\OpenCV, PCL.%
        \item Software development: GNU Make, CMake, GDB, Git, SVN.%
        \item Android: Java, C/C++ (NDK), RenderScript.%
        \item Web: PHP, JavaScript, AJAX.%
        \item Microsoft Office Suite and TeX/LaTeX.%
    \end{itemize}%
}%

\addskill%
{%
    \underline{Other interests}: hobbies and so on.
}%
